Relative Stable Maps in Genus One via Central Alignments

### 2018-02-09 genus-one-relative-maps.tex
Added some pictures to example

\begin{remark}
Trying to straighten out Gathmann's condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
\begin{equation} \label{eqn:eq_in_Pic}
(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
\end{equation}

@@

First we have to identify what the possible lifts of this object to the centrally aligned Li space are.

>>>>>>> navid

>>>>

\begin{remark}
Trying to straighten out Gathmann's condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
\begin{equation}\label{eqn:eq_in_Pic}
(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
\end{equation}

@@

First we have to identify what the possible lifts of this object to the centrally aligned Li space are. The map $C \to \mathfrak{X}$ takes the following form:

\begin{center}
\begin{tikzpicture}
\draw (-1,-1) -- (1,-1);
\draw (-1,-1) -- (-1,1);
\draw (1,-1) -- (1,1);
\draw (-1,1) -- (1,1);
\draw (-1,-1) -- (-2,-2.5);
\draw (-2,-2.5) -- (0,-2.5);
\draw (0,-2.5) -- (1,-1);
\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
\draw[red] (-1,-1.5) node[right]{$C_1$};
\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
\draw[red] (-0.6,-1) node[above]{$2$};

\draw[red,very thick] (0,-2.5) -- (0,-1);
\draw[red] (-0.1,-1.5) node[right]{$C_2$};
\draw[red,fill=red] (0,-1) circle[radius=2pt];
\draw[red] (0.1,-1) node[above]{$3$};

\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
\draw[red,very thick] (-0.25,-0.8) -- (0,1);
\draw[red] (0.1,0) node{$E$};
\draw[red,fill=red] (0,1) circle[radius=2pt] node[above]{$5$};
\end{tikzpicture}
\end{center}
(Here the box at level $1$ represents a single fibre of the expanded degeneration; $E$ is mapped into a fibre and has zero horizontal degree.) In this case $\tilde{C}$ is obtained from $C$ by bubbling a rational component at the marking, and so the map $\tilde{C} \to \mathfrak{X}$ is given by:

\begin{center}
\begin{tikzpicture}
\draw (-1,-1) -- (1,-1);
\draw (-1,-1) -- (-1,1);
\draw (1,-1) -- (1,1);
\draw (-1,1) -- (1,1);
\draw (-1,-1) -- (-2,-2.5);
\draw (-2,-2.5) -- (0,-2.5);
\draw (0,-2.5) -- (1,-1);
\draw (-1,1) -- (-1,3);
\draw (-1,3) -- (1,3);
\draw (1,3) -- (1,1);
\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
\draw[red] (-1,-1.5) node[right]{$C_1$};
\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
\draw[red] (-0.6,-1) node[above]{$2$};

\draw[red,very thick] (0,-2.5) -- (0,-1);
\draw[red] (-0.1,-1.5) node[right]{$C_2$};
\draw[red,fill=red] (0,-1) circle[radius=2pt];
\draw[red] (0.1,-1) node[above]{$3$};

\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
\draw[red,very thick] (-0.25,-0.8) -- (0,1);
\draw[red] (0.1,0) node{$E$};
\draw[red,fill=red] (0,1) circle[radius=2pt];
\draw[red] (-0.2,1) node[above]{$5$};

\draw[red, very thick] (0,1) -- (0,3);
\draw[red] (0,2) node[right]{$C_3$};
\draw[red,fill=red] (0,3) circle[radius=2pt] node[above]{$5$};
\end{tikzpicture}
\end{center}
